Evolution of the AGN UV luminosity function from redshift 7.5

### 2019-04-25 Paper/paper.tex
Update
Resubmitted version

After excluding the redshift bins that are most obviously affected by
systematic errors, the remaining redshift bins (filled symbols in
Figure~\ref{fig:evoln}) are consistent with a smooth redshift
evolution of the luminosity function parameters that may be described
by parametric models \citep{1976A&A....53...15M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2006AJ....131.2766R, 2007A&A...472..443B, 2009MNRAS.399.1755C,
  2013ApJ...773...14R, 2013A&A...551A..29P}.  Such descriptions have
also been developed in the literature for the X-ray
\citep[e.g.,][]{2015MNRAS.451.1892A} and so-called bolometric
luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.  Such
``global'' models of the QLF evolution are useful as
they give a continuous description of the luminosity function.  This
allows one to reduce the bias introduced by binning the data in
arbitrary redshift bins.  By potentially allowing for extrapolations
beyond the redshift range spanned by the data, such models are
valuable for understanding of the physics behind the luminosity
function.  Ideally, one would want to use physically meaningful
parameters that govern the formation and evolution of the AGN
population.  Unfortunately, such physical parameterisation is yet to
be developed.  We therefore set up an empirical parameterisation to
describe the evolution of the four parameters of the double power law
model in Equation~(\ref{eqn:dpl}) as 
\begin{align}
  &\phi_*(z) = F_0(\{c_{0,j}\}, z)\nonumber\\
  &M_*(z) = F_1(\{c_{1,j}\}, z)\nonumber\\
  &\alpha(z) = F_2(\{c_{2,j}\}, z)\nonumber\\
  &\beta(z) = F_3(\{c_{3,j}\}, z),
  \label{eqn:global}
\end{align}
where the $\{c_{n,j}\}$ are the new model parameters, and the $\{F_j\}$
are functions that vary smoothly with redshift $z$.  The joint
posterior probability distribution of these parameters can be now
written as
\begin{equation}
  p(\{c_{n,j}\} | \{M_i, z_i\}) \propto p(\{c_{n,j}\})p(\{M_i, z_i\} | \{c_{n,j}\}),
\end{equation}
where the likelihood 
\begin{equation}
  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_{n,j}\}),
\end{equation}
is now given by $\phi(M,z)$ with suitable normalisation.  Note that
$\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
parameters in that equation are redshift-dependent.  The negative
logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is a
straightforward generalisation of Equation~(\ref{eqn:S}).  We consider
models in which the evolution of the four double power law parameters
is modelled independently as in Equations~(\ref{eqn:global}), an
approach sometimes termed as ``flexible double power law''
\citep{2015MNRAS.451.1892A}.  We present three such models in this
paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
models differ in the way they describe the evolution of the faint-end
slope $\beta$ and in the selection of the AGN data.  The models are
defined as follows.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal_multiple()
  \end{center}
  \caption{AGN number density evolution in the global model, when the
    luminosity function is integrated (from top to bottom) down to
    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
    show the estimates from the our fiducual double power law
    luminosity function models in various redshift bins, with vertical
    error bars denoting one-sigma (68.26\%) uncertainties.  Open
    circles show the same in redshifts bins affected by systematics.
    Curves show the estimated density from the global models, with the
    accompanying shaded regions denoting the one-sigma uncertainty. }
  \label{fig:rhoqso}
\end{figure}

@@

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the posterior median values with one-sigma uncertainties
from the double power law fits to the data in redshift bins.  Solid
curves and shaded regions show the global models.  This number density
evolution again highlights the systematic error in data at $z\sim 3$.
The number density of AGN down to the limit of the deepest
spectroscopic surveys ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$
at its peak.  This density rapidly increases with redshift at low
redshifts and then drops with redshift gradually at high redshifts.
Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
which the number density of faint AGN peaks at lower redshifts than
that of the bright AGN \citep{2004ApJ...605..625H,
  2005MNRAS.360L..39N, 2006AJ....131.2766R, 2006A&A...451..443M,
  2009A&A...493...55E, 2013A&A...558A..89K, 2010MNRAS.401.2531A,
  2015MNRAS.451.1892A}.  While the number density of AGN with
$M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
spectroscopic data exist, $M_*<-21$, the number density of AGN peaks
at a slightly lower redshift.  However, the difference between our
three models is dramatically evident in Figure~\ref{fig:rhoqso}.
Model~1 prefers a decrease in the number density of faint quasars at
$z\sim 3$ followed by an increase at higher redshift.  This is caused
by the rapid steepening of the faint-end slope in this model at this
redshift (Figure~\ref{fig:evoln_global}).  Figure~\ref{fig:rhoqso}
reveals another property of these models: when extrapolated, the AGN
number density diverges in all three models at high redshifts.  This
results from the steep faint-end slope at high redshifts combined with
the rapid brightening of the break luminosity.  While no data exist at
redshift $z>7.5$, this divergent behaviour is shared by previous
models in the literature \citep{2007ApJ...654..731H}.
Figure~\ref{fig:rhoqso} also shows that although Models 2 and 3
exhibit regular behaviour in the evolution of the AGN number density
at $z\sim 3$, they do not fit the $z\sim 4$--$5$ data as well as Model
1.

\begin{table}
  \caption{Derived luminosity function evolution models.  These
    parameters are defined in Equations~(\ref{eqn:cbs}) and
    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
    details and the redshift range of validity of these models.
    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
    preferred model.}
  \label{tab:global}
  \begin{tabular}{p{1.0cm}eee}
    \hline 
    Param. &
    \multicolumn{1}{c}{Model 1} &
    \multicolumn{1}{c}{Model 2} &
    \multicolumn{1}{c}{Model 3} \\
    \hline
    $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
    $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
    $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
    \\
    $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
    $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
    $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
    $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
    \\
    $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
    $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
    \\
    $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
    $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
    $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
    $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
    $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
    \hline 
  \end{tabular}
\end{table}

@@

To account for redshift effects in the calculation of the \ion{H}{i}
photoionization rate, a continuous function
$\epsilon_{912}\left(z\right)$ is required. As our parametric QLF
models from the previous section suffer from non-monotonic or
divergent AGN number densities, we do not use them to derive the
corresponding $\epsilon_{912}\left(z\right)$, but instead fit the
individual emissivity values derived from credible data with a
five-parameter functional form used by \citet{2012ApJ...746..125H}
\begin{equation}
  \epsilon_{912}\left(z\right)=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}\quad,
  \label{eqn:e912fit}
\end{equation}
assuming a Gaussian likelihood for the emissivity values.  For
$M_{1450}<-18$ we obtain
\begin{multline}
  \epsilon_{1450}\left(z\right)=\left(10^{24.62}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.79}\\\times\frac{\exp(-1.23z)}{\exp(1.30z)+25.54}\quad,
  \label{eqn:e912_18}
\end{multline}
 and for $M_{1450}<-21$ we get
\begin{multline}
  \epsilon_{1450}\left(z\right)=\left(10^{24.37}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.11}\\\times\frac{\exp(-0.4z)}{\exp(1.98z)+25.42}\quad,
  \label{eqn:e912_21}
\end{multline}
where the parameter values are median values of marginalised posterior
distributions.  The 912\,\AA\ emissivity is then given by
Equation~(\ref{eqn:epsilon_912}).  The resultant curves and the
corresponding one-sigma uncertainties are shown in
Figure~\ref{fig:e912_2}.  Table~\ref{tab:gamma2} provides the derived
emissivities at 912\,\AA\ and 1450\,\AA\ together with their derived
errors at $0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Alex
Krolewski, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
Daniel Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
Venemans and Stephen Warren.  \new{We thank the anonymous referee for
  their comments.} GK acknowledges support from ERC Advanced Grant
320596 `The Emergence of Structure During the Epoch of Reionization'.

@@

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R},
    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}

@@

    0.31$^a$ & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.70^{+0.03}_{-0.02} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
    0.50$^a$ & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.01}_{-0.01} & 0.59^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
    0.72 & 0.60 & 0.80 & 1.73^{+0.05}_{-0.05} & 2.30^{+0.07}_{-0.07} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.03} \\
    0.91 & 0.80 & 1.00 & 2.84^{+0.15}_{-0.15} & 3.77^{+0.20}_{-0.20} & 2.10^{+0.05}_{-0.05} & 2.78^{+0.06}_{-0.06} \\
    1.10 & 1.00 & 1.20 & 3.73^{+0.11}_{-0.10} & 4.94^{+0.15}_{-0.14} & 2.91^{+0.05}_{-0.04} & 3.86^{+0.06}_{-0.05} \\
    1.30 & 1.20 & 1.40 & 5.72^{+0.25}_{-0.23} & 7.59^{+0.33}_{-0.31} & 4.46^{+0.10}_{-0.09} & 5.92^{+0.13}_{-0.12} \\
    1.50 & 1.40 & 1.60 & 7.05^{+0.22}_{-0.22} & 9.35^{+0.29}_{-0.29} & 5.60^{+0.09}_{-0.10} & 7.43^{+0.12}_{-0.13} \\
    1.71 & 1.60 & 1.80 & 7.71^{+0.19}_{-0.18} & 10.23^{+0.25}_{-0.24} & 6.70^{+0.10}_{-0.11} & 8.89^{+0.13}_{-0.15} \\
    1.98 & 1.80 & 2.20 & 10.64^{+0.35}_{-0.33} & 14.11^{+0.47}_{-0.44} & 7.93^{+0.14}_{-0.16} & 10.52^{+0.19}_{-0.21} \\
    2.30$^a$ & 2.20 & 2.40 & 10.20^{+0.24}_{-0.24} & 13.54^{+0.32}_{-0.32} & 8.91^{+0.13}_{-0.12} & 11.82^{+0.17}_{-0.16} \\
    2.45$^a$ & 2.40 & 2.50 & 8.04^{+0.26}_{-0.22} & 10.66^{+0.34}_{-0.29} & 7.17^{+0.14}_{-0.15} & 9.51^{+0.18}_{-0.20} \\
    2.55$^a$ & 2.50 & 2.60 & 6.63^{+0.19}_{-0.19} & 8.80^{+0.25}_{-0.25} & 6.21^{+0.12}_{-0.12} & 8.24^{+0.16}_{-0.16} \\
    2.65$^a$ & 2.60 & 2.70 & 6.59^{+0.16}_{-0.16} & 8.74^{+0.21}_{-0.21} & 6.47^{+0.17}_{-0.15} & 8.59^{+0.22}_{-0.20} \\
    2.75$^a$ & 2.70 & 2.80 & 7.46^{+0.20}_{-0.21} & 9.90^{+0.27}_{-0.28} & 7.20^{+0.19}_{-0.20} & 9.55^{+0.26}_{-0.27} \\
    2.85$^a$ & 2.80 & 2.90 & 7.96^{+0.32}_{-0.33} & 10.56^{+0.43}_{-0.43} & 7.53^{+0.31}_{-0.32} & 9.99^{+0.41}_{-0.42} \\
    2.95$^a$ & 2.90 & 3.00 & 7.93^{+0.41}_{-0.40} & 10.52^{+0.55}_{-0.53} & 6.84^{+0.20}_{-0.22} & 9.08^{+0.26}_{-0.29} \\
    3.05$^a$ & 3.00 & 3.10 & 7.22^{+0.41}_{-0.38} & 9.58^{+0.55}_{-0.51} & 6.27^{+0.23}_{-0.22} & 8.32^{+0.31}_{-0.29} \\
    3.15$^a$ & 3.10 & 3.20 & 9.93^{+1.12}_{-1.09} & 13.18^{+1.48}_{-1.45} & 7.03^{+0.35}_{-0.36} & 9.33^{+0.46}_{-0.48} \\
    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.84}_{-0.96} & 11.08^{+1.12}_{-1.28} & 6.17^{+0.38}_{-0.43} & 8.19^{+0.50}_{-0.57} \\

>>>>

After excluding the redshift bins that are most obviously affected by
systematic errors, the remaining redshift bins (filled symbols in
Figure~\ref{fig:evoln}) are consistent with a smooth redshift
evolution of the luminosity function parameters that may be described
by parametric models \citep{1976A&A....53...15M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2006AJ....131.2766R, 2007A&A...472..443B, 2009MNRAS.399.1755C,
  2013ApJ...773...14R, 2013A&A...551A..29P}.  Such descriptions have
also been developed in the literature for the X-ray
\citep[e.g.,][]{2015MNRAS.451.1892A} and so-called bolometric
luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.  Such
``global'' models of the QLF evolution are useful as
they give a continuous description of the luminosity function.  This
allows one to reduce the bias introduced by binning the data in
arbitrary redshift bins.  By potentially allowing for extrapolations
beyond the redshift range spanned by the data, such models are
valuable for understanding of the physics behind the luminosity
function.  Ideally, one would want to use physically meaningful
parameters that govern the formation and evolution of the AGN
population.  Unfortunately, such physical parameterisation is yet to
be developed.  We therefore set up an empirical parameterisation to
describe the evolution of the four parameters of the double power law
model in Equation~(\ref{eqn:dpl}) as 
\begin{align}
  &\log_{10}\phi_*(z) = F_0(\{c_{0,j}\}, z)\nonumber\\
  &M_*(z) = F_1(\{c_{1,j}\}, z)\nonumber\\
  &\alpha(z) = F_2(\{c_{2,j}\}, z)\nonumber\\
  &\beta(z) = F_3(\{c_{3,j}\}, z),
  \label{eqn:global}
\end{align}
where the $\{c_{n,j}\}$ are the new model parameters, and the $\{F_j\}$
are functions that vary smoothly with redshift $z$.  The joint
posterior probability distribution of these parameters can be now
written as
\begin{equation}
  p(\{c_{n,j}\} | \{M_i, z_i\}) \propto p(\{c_{n,j}\})p(\{M_i, z_i\} | \{c_{n,j}\}),
\end{equation}
where the likelihood 
\begin{equation}
  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_{n,j}\}),
\end{equation}
is now given by $\phi(M,z)$ with suitable normalisation.  Note that
$\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
parameters in that equation are redshift-dependent.  The negative
logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is a
straightforward generalisation of Equation~(\ref{eqn:S}).  We consider
models in which the evolution of the four double power law parameters
is modelled independently as in Equations~(\ref{eqn:global}), an
approach sometimes termed as ``flexible double power law''
\citep{2015MNRAS.451.1892A}.  We present three such models in this
paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
models differ in the way they describe the evolution of the faint-end
slope $\beta$ and in the selection of the AGN data.  The models are
defined as follows.

@@

\begin{figure}
  \begin{center}
    % \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_test2.pdf}
    % rhoqso.py -- draw_withGlobal_multiple()
  \end{center}
  \caption{\new{AGN number density evolution in the global model, when
      the luminosity function is integrated (from top to bottom) down
      to $M_\mathrm{1450}=-21, -24, -25.5$ and $-27$.  Points show the
      observed number density evolution, with vertical error bars
      denoting one-sigma (68.26\%) uncertainties.}  Curves show the
    estimated density from the global models, with the accompanying
    shaded regions denoting the one-sigma uncertainty. }
  \label{fig:rhoqso}
\end{figure}

@@

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  \new{Symbols show the number densities
  derived from the data.}  Solid curves and shaded regions show the
global models.  This number density evolution again highlights the
systematic error in data at $z\sim 3$.  \new{The number density of AGN
  down to the limit of the deepest spectroscopic surveys
  ($M_{1450}<-21$) is about few times $10^{-6}$ cMpc$^{-3}$ at its
  peak.  At higher redshifts, data go down to only about
  $M_{1450}=-24$.} This density rapidly increases with redshift at low
redshifts and then drops with redshift gradually at high redshifts.
Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
which the number density of faint AGN peaks at lower redshifts than
that of the bright AGN \citep{2004ApJ...605..625H,
  2005MNRAS.360L..39N, 2006AJ....131.2766R, 2006A&A...451..443M,
  2009A&A...493...55E, 2013A&A...558A..89K, 2010MNRAS.401.2531A,
  2015MNRAS.451.1892A}.  While the number density of AGN with
$M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
$M_*<-24$ peaks at $z\sim 2$.  However, the difference between our
three models is dramatically evident in Figure~\ref{fig:rhoqso}.
Model~1 prefers a decrease in the number density of faint quasars at
$z\sim 3$ followed by an increase at higher redshift.  This is caused
by the rapid steepening of the faint-end slope in this model at this
redshift (Figure~\ref{fig:evoln_global}).  Figure~\ref{fig:rhoqso}
reveals another property of these models: when extrapolated, the AGN
number density diverges in all three models at high redshifts.  This
results from the steep faint-end slope at high redshifts combined with
the rapid brightening of the break luminosity.  While no data exist at
redshift $z>7.5$, this divergent behaviour is shared by previous
models in the literature \citep{2007ApJ...654..731H}.

\begin{table}
  \caption{Derived luminosity function evolution models.  These
    parameters are defined in Equations~(\ref{eqn:cbs}) and
    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
    details and the redshift range of validity of these models.
    Errors indicate one-sigma (68.26\%) uncertainties. }
  \label{tab:global}
  \begin{tabular}{p{1.0cm}eee}
    \hline 
    Param. &
    \multicolumn{1}{c}{Model 1} &
    \multicolumn{1}{c}{Model 2} &
    \multicolumn{1}{c}{Model 3} \\
    \hline 
    $c_{0,0}$&-7.798^{+0.145}_{-0.157} &   -7.432^{+0.192}_{-0.211} &   -6.942^{+0.086}_{-0.086} \\
    $c_{0,1}$&1.128^{+0.085}_{-0.081} &    0.953^{+0.122}_{-0.107} &    0.629^{+0.046}_{-0.045} \\
    $c_{0,2}$&-0.120^{+0.005}_{-0.006} &   -0.112^{+0.007}_{-0.008} &   -0.086^{+0.003}_{-0.003} \\ 
    \\      
    $c_{1,0}$&-17.163^{+0.219}_{-0.226} &  -15.412^{+0.288}_{-0.318} &  -15.038^{+0.156}_{-0.150} \\
    $c_{1,1}$&-5.512^{+0.127}_{-0.124} &   -6.869^{+0.183}_{-0.169} &   -7.046^{+0.100}_{-0.101} \\
    $c_{1,2}$&0.593^{+0.011}_{-0.010} &    0.778^{+0.016}_{-0.015} &    0.772^{+0.013}_{-0.013} \\
    $c_{1,3}$&-0.024^{+0.00035}_{-0.00039} &   -0.032^{+0.001}_{-0.001} &   -0.030^{+0.001}_{-0.001} \\ 
    \\       
    $c_{2,0}$&-3.223^{+0.127}_{-0.121} &   -2.959^{+0.127}_{-0.143} &   -2.888^{+0.097}_{-0.093} \\
    $c_{2,1}$&-0.258^{+0.047}_{-0.051} &   -0.351^{+0.054}_{-0.052} &   -0.383^{+0.039}_{-0.041} \\
    \\       
    $c_{3,0}$&-2.312^{+0.034}_{-0.032} &   -2.264^{+0.038}_{-0.036} &   -1.602^{+0.029}_{-0.028} \\
    $c_{3,1}$&0.559^{+0.049}_{-0.045} &    0.530^{+0.054}_{-0.049} &    -0.082^{+0.009}_{-0.009} \\
    $c_{3,2}$&3.773^{+0.017}_{-0.016} &    2.379^{+0.118}_{-0.085} &  \multicolumn{1}{c}{---} \\        
    $c_{3,3}$&141.884^{+31.521}_{-8.832} & 12.527^{+7.349}_{-3.618} & \multicolumn{1}{c}{---} \\        
    $c_{3,4}$&-0.171^{+0.101}_{-0.116} &   -0.229^{+0.135}_{-0.150} & \multicolumn{1}{c}{---} \\
    \hline
  \end{tabular}
\end{table}

@@

To account for redshift effects in the calculation of the \ion{H}{i}
photoionization rate, a continuous function
$\epsilon_{912}\left(z\right)$ is required. As our parametric QLF
models from the previous section suffer from non-monotonic or
divergent AGN number densities, we do not use them to derive the
corresponding $\epsilon_{912}\left(z\right)$, but instead fit the
individual emissivity values derived from credible data with a
five-parameter functional form used by \citet{2012ApJ...746..125H}
\begin{equation}
  \epsilon_{912}\left(z\right)=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}\quad,
  \label{eqn:e912fit}
\end{equation}
assuming a Gaussian likelihood for the emissivity values.  For
$M_{1450}<-18$ we obtain
\begin{multline}
  \epsilon_{1450}\left(z\right)=\left(10^{24.72}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{8.42}\\\times\frac{\exp(-2.1z)}{\exp(1.09z)+38.56}\quad,
  \label{eqn:e912_18}
\end{multline}
 and for $M_{1450}<-21$ we get
 \begin{multline}
  \epsilon_{1450}\left(z\right)=\left(10^{23.91}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{8.26}\\\times\frac{\exp(-1.3z)}{\exp(1.62z)+13.6}\quad,
  \label{eqn:e912_21}
\end{multline}
where the parameter values are median values of marginalised posterior
distributions.  The 912\,\AA\ emissivity is then given by
Equation~(\ref{eqn:epsilon_912}).  The resultant curves and the
corresponding one-sigma uncertainties are shown in
Figure~\ref{fig:e912_2}.  Table~\ref{tab:gamma2} provides the derived
emissivities at 912\,\AA\ and 1450\,\AA\ together with their derived
errors at $0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.

@@

We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
especially for sharing their quasar selection functions.  It is a
pleasure to acknowledge useful discussions with James Aird, Eduardo
Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Enrico Garaldi,
Francesco Haardt, Martin Haehnelt, Paul Hewett, David Hogg, Vikram
Khaire, Sergey Koposov, Alex Krolewski, Donald Lynden-Bell, Roberto
Maiolino, Richard McMahon, Daniel Mortlock, Ewald Puchwein, Gordon
Richards, Alberto Rorai, Bram Venemans and Stephen Warren.  \new{We
  thank the anonymous referee for their comments.} GK acknowledges
support from ERC Advanced Grant 320596 `The Emergence of Structure
During the Epoch of Reionization'.

@@

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R},
    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}

@@

    0.31$^a$ & 0.10 & 0.40 & 0.41^{+0.01}_{-0.01} & 0.55^{+0.02}_{-0.02} & 0.27^{+0.01}_{-0.01} & 0.36^{+0.02}_{-0.01} \\
    0.50$^a$ & 0.40 & 0.60 & 0.72^{+0.01}_{-0.01} & 0.96^{+0.02}_{-0.02} & 0.53^{+0.01}_{-0.01} & 0.70^{+0.01}_{-0.01} \\
    0.72 & 0.60 & 0.80 & 2.03^{+0.08}_{-0.08} & 2.69^{+0.13}_{-0.11} & 1.22^{+0.02}_{-0.02} & 1.61^{+0.03}_{-0.03} \\
    0.91 & 0.80 & 1.00 & 3.64^{+0.23}_{-0.23} & 4.87^{+0.35}_{-0.37} & 2.33^{+0.06}_{-0.06} & 3.09^{+0.08}_{-0.08} \\
    1.10 & 1.00 & 1.20 & 4.47^{+0.16}_{-0.15} & 5.92^{+0.19}_{-0.19} & 3.18^{+0.05}_{-0.05} & 4.22^{+0.07}_{-0.07} \\
    1.30 & 1.20 & 1.40 & 7.33^{+0.38}_{-0.39} & 9.74^{+0.53}_{-0.53} & 5.10^{+0.12}_{-0.13} & 6.79^{+0.17}_{-0.18} \\
    1.50 & 1.40 & 1.60 & 8.84^{+0.35}_{-0.33} & 11.72^{+0.45}_{-0.48} & 6.32^{+0.13}_{-0.14} & 8.41^{+0.17}_{-0.17} \\
    1.71 & 1.60 & 1.80 & 9.05^{+0.26}_{-0.27} & 12.01^{+0.33}_{-0.32} & 7.51^{+0.13}_{-0.14} & 9.96^{+0.15}_{-0.15} \\
    1.98 & 1.80 & 2.20 & 14.27^{+0.53}_{-0.58} & 18.92^{+0.85}_{-0.79} & 9.40^{+0.19}_{-0.19} & 12.47^{+0.25}_{-0.24} \\
    2.30$^a$ & 2.20 & 2.40 & 10.20^{+0.25}_{-0.24} & 13.54^{+0.31}_{-0.31} & 8.88^{+0.11}_{-0.12} & 11.78^{+0.15}_{-0.17} \\
    2.45$^a$ & 2.40 & 2.50 & 8.05^{+0.23}_{-0.25} & 10.69^{+0.30}_{-0.30} & 7.16^{+0.14}_{-0.14} & 9.48^{+0.21}_{-0.19} \\
    2.55$^a$ & 2.50 & 2.60 & 6.60^{+0.20}_{-0.19} & 8.80^{+0.30}_{-0.28} & 6.22^{+0.13}_{-0.12} & 8.23^{+0.16}_{-0.16} \\
    2.65$^a$ & 2.60 & 2.70 & 6.56^{+0.16}_{-0.15} & 8.70^{+0.20}_{-0.21} & 6.44^{+0.16}_{-0.17} & 8.53^{+0.18}_{-0.22} \\
    2.75$^a$ & 2.70 & 2.80 & 7.47^{+0.22}_{-0.20} & 9.90^{+0.29}_{-0.26} & 7.19^{+0.18}_{-0.18} & 9.50^{+0.26}_{-0.26} \\
    2.85$^a$ & 2.80 & 2.90 & 7.90^{+0.30}_{-0.32} & 10.50^{+0.44}_{-0.43} & 7.50^{+0.28}_{-0.28} & 9.96^{+0.40}_{-0.38} \\
    2.95$^a$ & 2.90 & 3.00 & 7.96^{+0.37}_{-0.39} & 10.55^{+0.46}_{-0.47} & 6.85^{+0.20}_{-0.19} & 9.07^{+0.26}_{-0.25} \\
    3.05$^a$ & 3.00 & 3.10 & 7.25^{+0.42}_{-0.44} & 9.58^{+0.51}_{-0.56} & 6.22^{+0.20}_{-0.21} & 8.26^{+0.30}_{-0.29} \\
    3.15$^a$ & 3.10 & 3.20 & 9.91^{+1.14}_{-1.11} & 13.20^{+1.41}_{-1.32} & 6.99^{+0.35}_{-0.35} & 9.29^{+0.42}_{-0.42} \\
    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.88}_{-0.92} & 11.07^{+1.15}_{-1.26} & 6.10^{+0.36}_{-0.38} & 8.10^{+0.48}_{-0.53} \\
    3.34$^a$ & 3.30 & 3.40 & 12.19^{+2.77}_{-2.67} & 15.99^{+3.04}_{-3.34} & 7.30^{+0.79}_{-0.74} & 9.74^{+1.01}_{-1.10} \\
